\section{Introduction}
\label{sec:introduction}

Sustainable urban research often combines simulation, empirical analysis, and
multiple submission artifacts. That makes journal-specific formatting overhead a
real source of delay during initial submission and revision rounds. The
building-energy study in \cite{sokol2017validation} illustrates how clear
assumptions, documented archetypes, and reproducible supporting material remain
central to credible results.

This repository now treats the manuscript as a reusable submission package
rather than a one-off PDF build. The goal is to keep the scientific text in one
canonical source while generating the distinct files required by Elsevier's
double anonymized workflow.

\section{Methodology}
\label{sec:methodology}

The streamlined workflow separates shared manuscript content from
author-identifying metadata. A single manuscript source defines the title,
abstract, keywords, main sections, and bibliography, while profile-specific
wrappers determine whether author details are rendered.

Submission artifacts outside the manuscript itself are kept editable. The title
page, highlights, and optional graphical abstract each have dedicated source
files so the export package can be uploaded without manual repackaging.

\section{Results}
\label{sec:results}

The build interface now exposes one root command for the full paper, blind
paper, title page, highlights, export package, and cleanup steps. Validation is
performed before submission builds so common issues such as placeholder text,
missing citations, and highlight-length violations are caught early.

\section{Discussion}
\label{sec:discussion}

This structure reduces drift between manuscript variants because the body text
is edited once. It also keeps the repository aligned with Editorial Manager
upload constraints by flattening the final submission bundle to a single
directory level.

\section{Conclusion}
\label{sec:conclusion}

The repository is now prepared for migration of the real manuscript from
Overleaf or another LaTeX drafting environment. Replacing the sample text with
the real paper content should not require any structural changes to the build or
submission workflow.

\IfBlindTF{}{%
\section*{Acknowledgments}
The authors acknowledge the internal SustainLab review process that informed the
submission workflow.%
}
